TBA

### 2020-09-23 manuscript.tex

\subsection{\label{sec:Results}AT-all}

\subsubsection{\label{sec:Results}SRV optimization and analysis}

@@

\subsubsection{\label{sec:Results}SRV-MSM construction and optimization}

@@

\subsubsection{\label{sec:Results}Implied timescales for TICA-MSMs for }

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/AT-all_in_one.PNG}
        \caption{a) Thermo value calculated from Santalucia data and from MSMs b) TICA projections of freen energies and state clustering c) and transitions probabilities between states}
        \label{fig:AT-all_in_one}
	\end{center}
\end{figure}

\subsubsection{\label{sec:Results}Transition probabilities between states}

@@

For all proceeding sequences, we use the same SRV and MSM lag times, number of microstates, and cross-validation procedures as in the AT-all case. Although these might not represent fully optimized hyperparameters for each sequence, they preserve Markovian properties of the system and provide adequate resolution to evaluate macrostates \textcolor{purple}{not sure if this undermines the point I make earlier about building unique microstates and macrostates for each sequence so as to optimize the model}. The number of SRV coordinates and MSM macrostates are varied based on the kinetics and thermodynamics behavior of specific sequences.

@@

\subsection{\label{sec:Results}GC-end}

\subsubsection{\label{sec:Results}SRV-MSM construction and states}

@@

\subsubsection{\label{sec:Results}Comparison between GC-end and AT-all shifted states}

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/GC-end_in_one.PNG}
        \caption{a) Thermo value calculated from Santalucia data and from MSMs b) TICA projections of freen energies and state clustering c) and transitions probabilities between states \textcolor{Purple}{Need to fix 5' double shifted sequence, make same adjustments as for AT-all above}}
        \label{fig:GC-end_in_one}
	\end{center}
\end{figure}

\subsubsection{\label{sec:Results}Diffusion maps show sequence differences in shifted states}

@@

\subsubsection{\label{sec:Results}GC-end dynamics are largely two-state}

@@

\subsection{\label{sec:Results}GC-core}

\subsubsection{\label{sec:Results}Building SRV-MSM}

@@

\subsubsection{\label{sec:Results}Diffusion maps show ensemble of frayed states}

@@

\subsubsection{\label{sec:Results}SRV correlations to physical coordinates?}

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/GC-core_tracking_modes.png}
        \caption{Show how SRV coordinates correspond to physical features over time and during sample dissociation and hybridization events. Should probably go to SI if we also include GC-core diffusion maps \textcolor{purple}{These single trajectory figures have proven useful for visualizing SRV dynamics, could be employed for GC-mix comparisons as well}}
        \label{fig:GC-core_tracking_modes}
	\end{center}
\end{figure}

>>>>

\subsection{AT-all}

\subsubsection{SRV optimization and analysis}

@@

\subsubsection{SRV-MSM construction and optimization}

@@

\subsubsection{Implied timescales for TICA-MSMs for }

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/AT-all_in_one.PNG}
        \caption{a) Thermo value calculated from Santalucia data and from MSMs b) TICA projections of freen energies and state clustering c) and transitions probabilities between states}

        \label{fig:AT-all_in_one}
	\end{center}
\end{figure}

\subsubsection{Transition probabilities between states}

@@

For all proceeding sequences, we use the same SRV and MSM lag times, number of microstates, and cross-validation procedures as in the AT-all case. Although these might not represent fully optimized hyperparameters for each sequence, they preserve Markovian properties of the system and provide adequate resolution to evaluate macrostates \textcolor{magenta}{not sure if this undermines the point I make earlier about building unique microstates and macrostates for each sequence so as to optimize the model}. The number of SRV coordinates and MSM macrostates are varied based on the kinetics and thermodynamics behavior of specific sequences.

@@

\subsection{GC-end}

\subsubsection{SRV-MSM construction and states}

@@

\subsubsection{Comparison between GC-end and AT-all shifted states}

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/GC-end_in_one.PNG}
        \caption{a) Thermo value calculated from Santalucia data and from MSMs b) TICA projections of freen energies and state clustering c) and transitions probabilities between states \textcolor{magenta}{Need to fix 5' double shifted sequence, make same adjustments as for AT-all above}}
        \label{fig:GC-end_in_one}
	\end{center}
\end{figure}

\subsubsection{Diffusion maps show sequence differences in shifted states}

@@

\subsubsection{GC-end dynamics are largely two-state}

@@

\subsection{GC-core}

\subsubsection{Building SRV-MSM}

@@

\subsubsection{Diffusion maps show ensemble of frayed states}

@@

\subsubsection{SRV correlations to physical coordinates?}

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/GC-core_tracking_modes.png}
        \caption{Show how SRV coordinates correspond to physical features over time and during sample dissociation and hybridization events. Should probably go to SI if we also include GC-core diffusion maps \textcolor{magenta}{These single trajectory figures have proven useful for visualizing SRV dynamics, could be employed for GC-mix comparisons as well}}
        \label{fig:GC-core_tracking_modes}
	\end{center}
\end{figure}
